\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{color}
\usepackage{fullpage}

\def\xcolorversion{2.00}
\def\xkeyvalversion{1.8}

\usepackage[version=0.96]{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows, backgrounds, positioning, fit, shapes}
\usepackage[latin1]{inputenc}

\usepackage{algpseudocode}
\usepackage{algorithm}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{axiom}[theorem]{Axiom}

\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Example]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\begin{document}

\title{A discussion on Pleasure under Bucket Theory}

\author{
	Moitra, Subhodeep \\ 
	{\tt subhodeep.moitra@gmail.com}
	\and
	Ramachandran, Rohit\\
	{\tt omfgitsrohit@gmail.com}
}

\maketitle

\begin{abstract}
The end product of bucket theory is to derive pleasure at the Pleasure Caf\'e. An unsatisfying consequence from this theory is that the ``purpose'' of life is merely about ``pleasure''. In this article, we will lead a discussion about \textit{pleasure} and provide a rough mathematical model for creation and consumption of pleasure. We also attempt to illustrate the choices that we unconsciously make (1) Half Buckets vs Plunging (2) Hedonism vs Zen (3) Organic vs Forced. We hope that this discussion will bring to the forefront our unconscious choices and help us in leading a more deliberate and fulfilling life. 
\end{abstract} 

\section{Pleasure}
Pleasure is a catch all word to describe mental states that we find desirable. From a purely reductionist perspective it is nothing but a biochemical lightshow. One in which we are puppets pulled around by our genetic strings. We offer Theorem~\ref{mp2} $(MP^2 \; Theory)$ which attempts to put this biochemical puppetry in a more concrete setting. Every theory needs certain assumptions and we assume Axiom~\ref{compare-actions}. We make no claims that Bucket Theory~\cite{Bucket2014} is scientifically accurate, but merely a useful frame of reference to think about the human condition.

\begin{axiom}
\label{compare-actions}
Human beings evaluate actions by the amount of pleasure or pain it offers them.
\end{axiom}

\begin{definition}
An action is defined to be voluntary if a person chooses to take the action despite having the option of not taking it.
\end{definition}

\begin{theorem}
\emph{$(MP^2 \; Theory)$}
\label{mp2}
Every voluntary action has an underlying intent of maximizing pleasure or minimizing pain.
\end{theorem}

\begin{proof}
If a voluntary action did not have an underlying intent of maximizing pleasure or minimizing pain, then the person would be better off by not taking the action.
\end{proof}

\subsection{Multi-Nutrient Pleasures}
Not all pleasures are the same. Some pleasures are more intense than others while some others last longer. Each kind of pleasure has an necessary role without which our human experience is incomplete and left wanting. Bucket theory~\cite{bucket2014} defines three kinds of pleasures $ \mathcal{P} = \{peace, joy, thrill \}$ : 
\begin{enumerate}
\item Peace \& Tranquility $(P_{peace})$ .
\item Joy \& Happiness  $(P_{joy})$ .
\item Thrill \& Ecstacy $(P_{thrill})$
\end{enumerate}

$P_{peace}$ is a long lasting pleasurable state of mind ; $P_{joy}$ is a medium term pleasure that lasts a few days such as when taking a vacation or spending time with family ;  $P_{thrill}$ is much more short term lasting merely a few moments.  Each of these pleasures can be thought of as \textit{nutrients} that make up a balanced meal. Take away one of them and you will eventually fall sick.

\subsection{Mathematical Model}
The generation and consumption of pleasure happens in a harmonious cycle. 
Value $\rightarrow$ Control $\rightarrow$ Pleasure $\rightarrow$ Value $\rightarrow$ \ldots.
We attempt to model the creation and consumption of pleasure using a system of differential equations~(Equation \ref{eqn:diffeq}). Again, this is simply an illustrative exercise to put our intuitive ideas about bucket theory into a more concrete form. The variables $V_i(t),\; i\in \mathcal{V}$ correspond to the different value buckets. The value resources are converted into a control currency, $C(t)$. Control is then used to purchase the different pleasure nutrients $P_j(t) ; j\in \mathcal{P}$. This process is illustrated in Figure~\ref{fig:pleasure}.

\begin{align}\label{eqn:diffeq}
\frac{dC(t)}{dt}  &= \sum_{i \in \mathcal{V}}\alpha_i V_i(t) - \sum_{j \in \mathcal{P}}\beta_j C(t)\\
\frac{dP_j(t)}{dt}  &= \beta_j C(t) - \sum_{i \in \mathcal{V}}\gamma_{ij}V_j(t) \\
\frac{dV_i(t)}{dt}  &= \sum_{j \in \mathcal{P}}\gamma_{ij}P_j(t) - \alpha_i V_i(t)
\end{align}

\begin{figure}
\centering
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3cm,thick,
  pleasure node/.style={circle,fill=red!20,draw,font=\sffamily\bfseries},
  blank node/.style={circle,fill=blue!20,fill opacity=0,font=\sffamily\bfseries},
  bucket/.style={draw, fill=blue!20, minimum height=3em, minimum width=4em, cylinder, shape border rotate=90, shape aspect=0.1}]


    \node [bucket] (Vw)                                    {$V_{work}(t)$};
    \node [bucket] (Vf) [below of=Vw]                      {$V_{family}(t)$};

    \node [bucket, minimum height=5em, minimum width=4em, fill=green!20] (C) [right of=Vw, yshift = -15mm]                         {$C(t)$};


    \node [pleasure node] (Pj) [right of=C]                      {$P_{joy}(t)$};
    \node [pleasure node] (Pp) [above of=Pj]                       {$P_{peace}(t)$};
    \node [pleasure node] (Pt)  [below of=Pj] 					 {$P_{thrill}(t)$};

 \path[every node/.style={font=\sffamily\small}]
    (Vw) edge node [below] {$\alpha_w$} (C)
    (Vf) edge node [above]   {$\alpha_f$} (C)

    (C) edge  node [below] {$\beta_p$} (Pp)
     edge node [above]   {$\beta_j$} (Pj)
     edge  node [above] {$\beta_t$} (Pt)

	(Pp) edge [bend right] node [above] {$\gamma_{pw}$} (Vw)
	 edge [bend right] node [above] {$\gamma_{pf}$} (Vf)
	 
	(Pj) edge [bend right] node [above] {$\gamma_{jw}$} (Vw)
	 edge [bend left] node [below] {$\gamma_{jf}$} (Vf)
	 
	(Pt) edge [bend left] node [below] {$\gamma_{tw}$} (Vw)
	 edge [bend left] node [below] {$\gamma_{tf}$} (Vf);

  \begin{pgfonlayer}{background}
    \filldraw [line width=4mm,join=round,black!10]
      (Vw.north  -| Vw.east)  rectangle (Vf.south  -| Vf.west)
      (C.north  -| C.east)  rectangle (C.south  -| C.west)
      (Pp.north  -| Pp.east)  rectangle (Pt.south  -| Pt.west);
  \end{pgfonlayer}
\end{tikzpicture}
\caption{A simple instance of Bucket Theory. There are two value buckets $\mathcal{V}=\{work,family\}$, the control bank $C$ and three nutrients at the pleasure Caf\'e $\mathcal{P}=\{peace, joy, thrill\}$.  The value resources are converted into a control currency, $C(t)$. Control is then used to purchase the different pleasure nutrients $P_j(t) ; j\in \mathcal{P}$. }
\label{fig:pleasure}
\end{figure}

\subsection{Half Buckets vs Plunging}
The control factory~\cite{Bucket2014} holds several different recipes.


\subsection{Hedonism vs Zen}

\subsection{Organic vs Forced}


\end{document}